\section{Introduction}

Today, authorities in Vancouver and New York City are considering implementing tolls on zones of their downtown street networks as a means of relieving traffic congestion---a practice we will call ``downtown congestion pricing'' (DCP). Forms of congestion pricing are already in place on highways and bridges throughout North America, such as Highway 407 in Toronto and the High-Occupancy Toll (or ``Express'') Lanes now proliferating across the United States. But the schemes being considered for New York City and Vancouver would differ from not only by their setting but also topologically: while congestion pricing on highways charges drivers to travel between well-defined start and end points, DCP charges for use of  clusters of contiguous downtown streets (``zones''); charged trips can thus begin and end at numerous points within the zone or along its boundary. Thus, DCP is attended by administrative and technological concerns that warrant special treatment.

To date, only five cities have implented DCP as we have defined it: Singapore, London, Stockholm, Gothenburg and Milan. This paper provides a broad sweep of their experiences along with some historical connective tissue. The goal is to help the reader quickly become familiar with the experience of DCP thus far and to point toward works containing further information. Similarly, \citet{Hau1992}, \citet{Gomez-Ibanez1994}, \citet{Small1998} and \citet{Anas2011} survey various congestion pricing schemes up to their publications, with \citet{Gomez-Ibanez1994} being especially thorough, but this paper includes later developments and emphasizes the special concerns of downtown schemes.

\subsection{Organization and scope}

We describe six DCP schemes: Singapore's Area License Scheme (\ref{sec:als}), Singapore's Electronic Road Pricing (Sec. \ref{sec:erp}), the London Congestion Charge (Sec. \ref{sec:london}), the Stockholm Congestion Tax (Sec. \ref{sec:stockholm}), Milan's Ecopass and Area C\footnote{These are treated together as Area C is technologically the same as Ecopass but has different prices and exemptions.} (Sec. \ref{sec:milan}) and the Gothenburg Congestion Tax (Sec. \ref{sec:gothenburg}). Each description includes four subsections:

\begin{enumerate}
    \item \emph{Implementation}. Motivation and events leading up to implementation.
    \item \emph{Design}. The scheme's technology, prices, exemptions and geography---including changes over time.\footnote{In these sections, details about scheme design comes from the schemes' official websites except when otherwise noted.}
    \item \emph{Transportation Impacts}. Impact on travel---especially on the magnitude and composition of flow into the charged zone and, where available, on speeds and transit ridership. Note that DCP also affects air pollution, equity, real estate and commerce. But the transportation impacts are the most well documented, comparable and, arguably, \emph{direct} impacts. The reader interested in other effects---which are undoubtedly important---can usually find such information in the works cited.
    \item \emph{Finances}. How much money the scheme has cost to build and operate, and how much revenue it has raised.
\end{enumerate}

In between are sections devoted to historical context. Sec. \ref{sec:early} describes intelletual developments prior to real implementation. Sec. \ref{sec:transition} describes a twenty-year ``transition period'' following Singapore's first scheme. Sec. \ref{sec:future} briefly describes future plans. 

Note that, for brevity and focus, certain developments in the history of DCP have been omitted. For example, Valetta, Malta \citep{Attard2010} and Durham, England \citep[p.269]{Santos2006a} also apply tolls to central areas, but these schemes are very small and not much data is collected on their outcomes. 

% Likewise, about ten schemes were proposed but languished or been cancelled (including Hong Kong, Edinburgh, Manchester, New York City, San Francisco, Cambridge, the Randstadt region of the Netherlands and Helsinki), but among these only Hong Kong's is discussed, because it provides context for Singapore's ERP.

\subsection{Themes}\label{ssec:themes}

The paper is more focused on description than inference, but we do point out two recurring themes.

Theme I is that exemptions are among the most consequential aspects of a scheme's design, to a degree that often surprises authorities. Exempt classes of trips or vehicles quickly become a large share of traffic, and in doing so they compromise congestion goals and reduce revenue more than projected.

Theme II is that charging implementing a toll is much more consequential than differences in the toll level. When a scheme is implemented, entries to the tolled zone by vehicles subject to charge drop sharply, but later toll increases make only a minor difference. Noting this effect in Stockholm and Gothenburg, \citet[p. 45]{Borjesson2018} offer two explanations. The first is grounded in traditional economic theory: the initial toll discourages all the drivers with elastic demands, so the traffic exposed to later toll increases is composed of drivers with a high willingness-to-pay for travel. The second explanation is grounded in behavioral economics: \citet{Shampanier2007} note that consumers are extremely sensitive to being charged \emph{any} positive price---even negligible ones.

